Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

\subsubsection{PRA Engine Implementation}
Before implementing the solution, we  must first
select the tools that will be used to do the implementation. In general, there are many programming languages that can implement solutions of the PRA Engine. However, there is
an important need to implement the Kolmogorov-Smirnov (K-S) statistical test which not all programming languages have a support library to do this. There are two programming languages that have libraries for performing K-S tests
which are the Go and Python programming languages. The Go language has the Gonum\footnote{\url{gonum.org}} library which
has a K-S test implementation in the \texttt{KolmogorovSmirnov} function, while the language
Python has the SciPy\footnote{\url{scipy.org}} library which has a K-S test implementation in the \texttt{scipy.stat.ks\textunderscore 2samp} function.

>>>>

%\subsubsection{PRA Engine Implementation}
Before implementing the solution, we  must first
select the tools that will be used to do the implementation. In general, there are many programming languages that can implement solutions of the PRA Engine. However, there is
an important need to implement the Kolmogorov-Smirnov (K-S) statistical test which not all programming languages have a support library to do this. There are two programming languages that have libraries for performing K-S tests
which are the Go and Python programming languages. The Go language has the Gonum\footnote{\url{gonum.org}} library which
has a K-S test implementation in the \texttt{KolmogorovSmirnov} function, while the language
Python has the SciPy\footnote{\url{scipy.org}} library which has a K-S test implementation in the \texttt{scipy.stat.ks\textunderscore 2samp} function. From the two languages, we finally decide to choose Python language to implement the solution after successfully parsed the Zipkin trace data with Object-oriented Programming approach based on source code owned by Zipkin's User Interface application using the Javascript language.
